\textsc{LiveRec}: Framing Debug Protocols to Hotwire Probes

### 2023-09-28 paper/paper.tex
Change some figures

\begin{figure}[h]
  \centering
  \includegraphics[width=0.8\linewidth]{img/architecture.png}
  \caption{General architecture (placeholder)}
  \label{fig:architecture}
\end{figure}
%vRozen: todo fixme remove 'placeholder'
%vRozen: perhaps a tikz image here

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=0.6\linewidth]{img/stackrecording_impl.png}
  \caption{Record Stackrecording (placeholder)}
  \label{fig:stack-recording-impl}
\end{figure}
%vRozen: This is a UML sequence diagram.
%vRozen: The loop may use an activation frame.
%vRozen: The objects (or component instances) on the top of life lines appear in rectangular boxes.

>>>>

\begin{figure}[h]
  \centering
  \includegraphics[width=0.8\linewidth]{img/architecture_2.png}
  \caption{General architecture}
  \label{fig:architecture}
\end{figure}
%vRozen: todo fixme remove 'placeholder'
%vRozen: perhaps a tikz image here

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=0.8\linewidth]{img/uml_sequence_record.png}
  \caption{Record Stackrecording}
  \label{fig:stack-recording-impl}
\end{figure}

\begin{comment} %Mermaid
sequenceDiagram
    participant A as Live Probes server
    participant B as Debugger (KAA)
    A->>B: Execute method(args)
    B->>A: Breakpoint at method entry
    loop Until method end
        A->>B: request stackframe
        B->>A: stackframe
        A->>B: request step
        B->>A: hit breakpoint
    end
\end{comment}
%vRozen: This is a UML sequence diagram.
%vRozen: The loop may use an activation frame.
%vRozen: The objects (or component instances) on the top of life lines appear in rectangular boxes.
